
\begin{thebibliography}{99}
%\addcontentsline{toc}{chapter}{Literaturverzeichnis}
\addcontentsline{toc}{chapter}{Bibliography}



\bibitem {he} {\sc R. He, A. Bachrach, M. Achtelik, A. Geramifard, D. Gurdan, S. Prentice,
J. Stumpf, and N. Roy}: 
{\it On the design and use of a micro air
vehicle to track and avoid adversaries}. The Int. Journal of Robotics
Research, vol. 29, pp. 529-546, 2010.


\bibitem {colling} {\sc D. Colling, O. A.~Yakimenko, J. F.~Whidborne, and A. K.~Cooke}:
{\it A prototype of an autonomous controller for a quadrotor UAV}. In
Proceedings of the European Control Conference, Kos, Greece, 2007,
pp. 1-8.


\bibitem {hehn} {\sc M. Hehn and R. D'Andrea }:
{\it Quadrocopter trajectory generation and control}. In
International Federation of Automatic Control (IFAC), World Congress 2011, 2011.


\bibitem {lup} {\sc S. Lupashin, A. Schollig, M. Sherback, and R. D'Andrea}:
 {\it A simple learning strategy for high-speed quadrocopter multi-flips}.
In Proc. of the IEEE Int. Conf. on Robotics and Automation, Anchorage, AK,
May 2010, pp. 1642-1648.


\bibitem {bou} {\sc Y. Bouktir, M. Haddad, and T. Chettibi}:
{\it Trajectory Planning for a
Quadrotor Helicopter}. In Mediterranean Conference on Control and
Automation, Jun. 2008, pp. 1258-1263


\bibitem {mellinger} {\sc D. Mellinger and V. Kumar}: 
{\it Minimum snap trajectory generation and
control for quadrotors}. In International Conference on Robotics and
Automation, 2011, pp. 2520-2525.

\bibitem {lik} {\sc M. Likhachev, G. Gordon and S. Thrun}: 
{\it  ARA*: Anytime A* with Provable Bounds on Sub-Optimality }.
Advances in Neural Information
Processing Systems, vol. 16, 2003

\bibitem {richter} {\sc C. Richter,  A. Bry, and N, Roy}: 
{\it  Polynomial Trajectory Planning
for Quadrotor Flight}.
In International Conference on Robotics and
Automation, 2013.

\bibitem {NLopt} {\sc NLopt}: 
{\it NLopt, an open-source library for nonlinear optimization.}\newline
\href{http://ab-initio.mit.edu/wiki/index.php/NLopt}{$http://ab-initio.mit.edu/wiki/index.php/NLopt$}

\bibitem {OctoMap} {\sc A. Hornung, K. M. Wurm, M. Bennewitz, C. Stachniss, and W. Burgard}: 
{\it OctoMap: An efficient probabilistic 3D mapping framework based on octrees}.
Autonomous Robots, 2013.

\bibitem {ROS} {\sc ROS}: 
{\it The Robot Operating System (ROS) is a set of software libraries and tools for robot applications.}\newline
\href{http://www.ros.org/}{$http://www.ros.org/$}

\bibitem {Eigen} {\sc Eigen}: 
{\it  A C++ template library for linear algebra: matrices, vectors, numerical solvers, and related algorithms.}\newline
\href{http://eigen.tuxfamily.org/index.php?title=Main_Page}{$http://eigen.tuxfamily.org/index.php?title=Main_Page$}

\bibitem {Vicon} {\sc Vicon}: 
{\it Vicon Tracker is a powerful object tracking solution providing unrivaled data accuracy for integration in to 3D applications.}\newline
\href{http://www.vicon.com/}{$http://www.vicon.com/$}

\end{thebibliography}
